\subsection{System Design}

Write what the system does each round of the simulation.

\subsubsection{Agent Types}

There are 4 agent types that have been implemented for both of the multi-agent systems.
These are the minimum number of agents types to allow the benchmarks to be run.

The first agent type is the Clock agent.
This agent is not apart of the supply chain simulation, but instead keeps track of the simulation itself.
It makes sure all the agents are ready before starting the simulation.
While the simulation is running, the Clock agent keeps track of what round the simulation is currently on and which agents are already finished.
TODO\@: Mention how the Clock agent is used to measure the benchmarks.

The second type of agent is the Producer agent.
This agent produces the raw goods or components that can be manufactured into finished PCs.
The Producer agent ignores any messages it receives from the consumer agent as messages from it are not relevant to the Producer agent.
It also ignores messages from other Producer agents as they would not be relevant to it.
This agent responds to messages from the Manufacturer agent about requests to buy components.
If the request is for a reasonable amount of components and the price per component is acceptable, then the Producer agent will accept the request.
There can be more than one Producer agent per experiment.

The next type of agent is the Manufacturer agent.
This agent takes requests for finished PCs from the Consumer agent and attempts to fulfill them buy ordering components from Producer agents.
It will reject requests from the Consumer agent if they are at a too low price or request too many finished PCs in too short of a time frame.
This is the most complex agent type as it has to interact with both the Consumer agent and potentially multiple Producer agents.
As such there will only be one Manufacturer agent in the simulation.

The final agent type is the Consumer agent.
This agent makes a number of requests to buy finished PCs from the Manufacturer agent each round.
It will offer to buy a certain number of PCs at a given price and any offers that are not accept during the next round will be regarded as being rejected.
The Consumer agent ignores all messages from the Producer agent as it does not care about raw goods.
There will only ever be one Consumer agent as adding multiple agents would just result in there being too many orders for the Manufacturer agent to fulfill.

\subsubsection{Simulation Rounds}

Add message sequence diagram for a typical round of the simulation.
